### 2022-09-02 Bloods Data Sheet.Rmd
Dz export along with new LMM

#Summary Data
```{r}
BlaSUM <- main_df%>%
summarySE(measurevar = "Bla", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

@@

>>>>

#Summary Data
```{r}
BlaSUM <- main_df2%>%
summarySE(measurevar = "Bla", groupvar =c("Session", "Speed", "BFR", "Time_Point", "Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

@@

```{r}
write.csv(BlaSUM,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\BLA_sum (02-09-2022).csv",row.names = FALSE)
```

### 2022-09-02 Bloods_LMM.Rmd
Dz export along with new LMM

```{r}
names(LDH_PCHANGE_CL)
```

>>>>

```{r}
names(main_df2)

```

#Sodium
```{r}
NaLMM <- lmer(cal_Na ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(NaLMM)
pairwise_NaLMM <- emmeans(NaLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_NaLMM
```

```{r}
tab_model(NaLMM)
```

#Potassium
```{r}
KLMM <- lmer(cal_K ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(KLMM)
pairwise_KLMM <- emmeans(KLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_KLMM
```

```{r}
tab_model(KLMM)
```

#Chlorine

```{r}
ClLMM <- lmer(cal_Cl ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(ClLMM)
pairwise_ClLMM <- emmeans(ClLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_ClLMM
```

```{r}
tab_model(ClLMM)
```
